JMS

### 2021-03-30 analysis.Rmd
analysis simulation data

setwd("C:/Users/rocpa/OneDrive/Desktop/AF2/exp12_2020/")

# Back work, used to combine datasets from diffent runs. To IGNORE OR DELETE

# etlib_min1 <- read.csv("mj_etlib_min.csv",skip = 6)
# etlib_min2 <- read.csv("mj_etlib_min2.csv",skip = 6)
# etlib_min <- rbind(etlib_min1,etlib_min2)
# names(etlib_min) <- pull(read.csv("legend_sec_etlib.csv"))
# etlib_min <- cbind(ID = "etlib_min",etlib_min)

basic <- read.csv("df_basic.csv",sep =",")
value_basic <- read.csv("df_valuebasic.csv",sep = ",")
asym_dom <- read.csv("df_asym_dom.csv",sep = ",")
dislib <- read.csv("df_dislib.csv", sep = ",")
sa_asym <- read.csv("df_sa_asym.csv",sep =",")
etlib <- read.csv("df_etlib.csv",sep =",")

@@

```{r heatmap, include=TRUE, fig.cap="Comparison dominant vs secondary", echo=FALSE}

excl <- names(basic) %in% c("run", "ID","density","step")
basic_sa <- basic[!excl]  %>% group_by(dominant,secondary,circle_orange,circle_blue,fraction_blue) %>% summarise_all(c("mean"= mean,"sd"= sd))

data_f <- basic_sa %>% filter(dominant >= secondary)   %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
 `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ), 
 `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))

```{r basefigure, fig.width=30, fig.cap="Same parameter for ethnic and value homophily for all agents", echo=FALSE}

# database filter
excl <- names(basic) %in% c("run", "ID","density","step")
basic_sa <- basic[!excl] %>% filter(dominant == secondary) %>% group_by(dominant,secondary,circle_orange,circle_blue,fraction_blue) %>% summarise_all(c("mean"= mean,"sd"= sd))

@@

```{r secondary_0, fig.width=30, fig.cap="secondary preference set to 0", echo=FALSE}

@@

```{r sensval, fig.width=30, fig.cap="Test mechanism: increase liberal and conservative, all other 0", echo=FALSE}

@@

```{r sens_secondary, fig.width=30, fig.cap="Test mechanism: increase secondary preference, all determinism high", echo=FALSE}

@@

```{r asym, fig.width=30, fig.cap="Baseline asymmetric conditions", echo=FALSE}

@@

fig_prox <- ggplot(data = data_prox, aes(x = dominant, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
  geom_vline(xintercept = 20, color = "red") +
  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab("Spatial Proximity") + 
  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

@@

```{r dislib, fig.width=30, fig.cap="Effect distribution liberal minority, asymmetric based condition", echo=FALSE}

@@

fig_prox <- ggplot(data = data_prox, aes(x = circle_orange, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(10,90 ,by = 10))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks = seq(0,max(data_prox$Prox), by = 0.5)) +
   geom_vline(xintercept = 50, color = "red") +
 scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab("Spatial Proximity") + 
theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

@@

```{r sa_dom_50prox, fig.width=30, fig.cap="Sensitivity proximity ethnic conservative local, baseline asymmetric conditions", echo=FALSE}

@@

  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab("Spatial Proximity") + 
  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

@@

```{r sa_vllblc,  fig.cap="Sensitivity proximity value liberal locals, distribution liberals", echo=FALSE}

>>>>

# fig.cap in the titles of chunk reports figure number in the text
# Each chunk reports code for dataset filter, summary: mean and standard deviation, plotting graph, raw material latex, output details. They can vary if image was combined or other tweaks needed
# Fig. 9 (sensitivity to group-type preference) selects distribution liberals 50% and combines for 4 group-type
# Outputs create folder "image" for images and "latex" for latex raw tables
# Name of index (often used in y-lab and in table): exposure for ethnic symmetric, spatial proximity or exposure correct for ethnic asymmetric

# Change work directory in quotes
setwd("C:/Users/rocpa/OneDrive/Desktop/AF2/exp12_2020/")

# Datasets

basic <- read.csv("df_basic.csv",sep =",")                 # basic condition
value_basic <- read.csv("df_valuebasic.csv",sep = ",")     # value basic
asym_dom <- read.csv("df_asym_dom.csv",sep = ",")          # asymmetric conditions, baseline figure dominant preference
dislib <- read.csv("df_dislib.csv", sep = ",")             # sensitivity to distribution of liberals
sa_asym <- read.csv("df_sa_asym.csv",sep =",")             # sensitivity analysis, ethnic asymmetry
etlib <- read.csv("df_etlib.csv",sep =",")                 # ethnic preference liberals, ethnic asymmetry
asym_all <- read.csv("df_asym_all.csv",sep =",")           # baseline ethnic  asymmetry

# for labels

@@

# Symmetric Conditions

```{r basefigure, fig.width=30, fig.cap="Fig. 3 Baseline symmetric. Same parameter for ethnic and value homophily for all agents", echo=FALSE}

# database filter AND summary mean and standard deviation
excl <- names(basic) %in% c("run", "ID","density","step")
basic_sa <- basic[!excl] %>% filter(dominant == secondary) %>% group_by(dominant,secondary,circle_orange,circle_blue,fraction_blue) %>% summarise_all(c("mean"= mean,"sd"= sd))

@@

```{r secondary_0, fig.width=30, fig.cap="Fig. 4 Secondary preference set to 0. Baseline symmetric", echo=FALSE}

@@

```{r sensval, fig.width=30, fig.cap="Fig. 5 Test mechanism: increase liberal and conservative, all other 0. Baselie  symmetric", echo=FALSE}

@@

```{r sens_secondary, fig.width=30, fig.cap="Fig. 6 Test mechanism: increase secondary preference, all determinism high. Baseline symmetric", echo=FALSE}

@@

```{r heatmap, include=TRUE, fig.cap="Fig. 7 Heatmap dominant vs secondary. Baseline symmetric", echo=FALSE}

# database filter
excl <- names(basic) %in% c("run", "ID","density","step")
basic_sa <- basic[!excl]  %>% group_by(dominant,secondary,circle_orange,circle_blue,fraction_blue) %>% summarise_all(c("mean"= mean,"sd"= sd))

# data preparation: long format
data_f <- basic_sa %>% filter(dominant >= secondary)   %>% gather(key= subgroup, value = Segra, et_sq_bl_mean, vl_sq_bl_mean, et_cl_bl_mean, vl_cl_bl_mean, et_sq_or_mean, vl_sq_or_mean, et_cl_or_mean, vl_cl_or_mean) %>% mutate(
  `segregation` = fct_relevel(fct_collapse(subgroup,"ethnics" = c("et_sq_bl_mean","et_cl_bl_mean","et_sq_or_mean","et_cl_or_mean"), "values" = c("vl_sq_bl_mean","vl_cl_bl_mean","vl_sq_or_mean","vl_cl_or_mean")),"ethnics"),
 `orientation` = fct_relevel(fct_collapse(subgroup, "conservative" = c("et_sq_bl_mean","vl_sq_bl_mean","et_sq_or_mean","vl_sq_or_mean"), "liberal" = c("et_cl_bl_mean","vl_cl_bl_mean","et_cl_or_mean","vl_cl_or_mean")),"conservative" ), 
 `ethnia` = fct_relevel(fct_collapse(subgroup, "local" = c("et_sq_bl_mean","vl_sq_bl_mean","et_cl_bl_mean","vl_cl_bl_mean"),"minority" = c("et_sq_or_mean","vl_sq_or_mean","et_cl_or_mean","vl_cl_or_mean")), "local"))

# Asymmetric Conditions

```{r asym, fig.width=30, fig.cap="Fig. 8 Baseline asymmetric conditions, secondary = 0", echo=FALSE}

@@

fig_prox <- ggplot(data = data_prox, aes(x = dominant, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
  geom_vline(xintercept = 20, color = "red") +
  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

@@

```{r sa_dom_50prox, fig.width=30, fig.cap="Fig. 9, Sensitivity analysis group-type. Each panel reports 50 % then combined", echo=FALSE}

  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 12)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13),plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

```{r dislib, fig.width=30, fig.cap="Fig. 10, Effect distribution liberals minority, asymmetric condition", echo=FALSE}

@@

fig_prox <- ggplot(data = data_prox, aes(x = circle_orange, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(10,90 ,by = 10))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks = seq(0,max(data_prox$Prox), by = 0.5)) +
   geom_vline(xintercept = 50, color = "red") +
 scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

@@

```{r sa_vllblc,  fig.cap="Fig 11, Sensitivity value liberals majority - exposure correct, asymmetric conditions", echo=FALSE}

 scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
  geom_vline(xintercept = 1, color = "red") +
   xlab(expression(Exposure[correct])) + ylab("Exposure") +
  theme_bw() + theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

prox_pic <- ggplot(data = data_prox, aes(x = val_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
 facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    strip.text = element_text(size=13),
    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

```{r sa_vllbmn,  fig.cap="Fig. 12: Sensitivity value liberals minority - exposure correct, asymmetric conditions", echo=FALSE}

# for image output

# ethnic exposure plot

 scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
  geom_vline(xintercept = 1, color = "red") +
   xlab(expression(Exposure[correct])) + ylab("Exposure") +
  theme_bw() + theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

# exposure corrected plot

prox_pic <- ggplot(data = data_prox, aes(x = val_lib_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
 facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
    geom_vline(xintercept = 20, color = "red") +  geom_hline(yintercept = 1, color = "red") +
  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    strip.text = element_text(size=13),
    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

```{r et_lib_loc,  fig.cap="Fig. 13: Ethnic liberals majority, asymmetric conditions", echo=FALSE}

 scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
  geom_vline(xintercept = 1, color = "red") +
  xlab(expression(Exposure[correct])) +  + ylab("Exposure") +
  theme_bw() + theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

prox_pic <- ggplot(data = data_prox, aes(x = eth_lib_loc, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
 facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
    geom_vline(xintercept = 0, color = "red") +  geom_hline(yintercept = 1, color = "red") +
  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    strip.text = element_text(size=13),
    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

```{r et_lib_min,  fig.cap="Fig. 14: Ethnic liberals minority, asymmetric conditions", echo=FALSE}

 scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
  geom_vline(xintercept = 1, color = "red") +
  xlab(expression(Exposure[correct])) + ylab("Exposure") +
  theme_bw() + theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

prox_pic <- ggplot(data = data_prox, aes(x = eth_lib_min, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
 facet_wrap(~ circle_orange, dir = "v", labeller = labeller(circle_orange = circle_orange.labs)) +
    geom_vline(xintercept = 0, color = "red") +  geom_hline(yintercept = 1, color = "red") +
  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
   scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    strip.text = element_text(size=13),
    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 14),
    plot.title=element_text(hjust = 0.5), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

```{r asym_ALL, fig.width=30, fig.cap="Fig. 16 Baseline asymmetric conditions, dominant preferene ==  secondary preference", echo=FALSE}

# database filter
excl <- names(asym_all) %in% c("run", "density","step")
dataset_sa <- asym_all[!excl] %>% group_by(dominant,circle_orange,circle_blue,fraction_blue) %>% summarise_all(c("mean"= mean,"sd"= sd))

xlab_t <- "ß dominant = ß secondary"

row_exp <- c("\\multicolumn{17}{|c|}{Ethnic asymmetric condition: Exposure}  \\\\\\hline\n",
   "Preference &  \\multicolumn{8}{|c|}{Ethnic Exposure} & \\multicolumn{8}{|c|}{Value Exposure}   \\\\\\hline\n",
  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
"$\\beta$ sec = $\\beta$ doom  & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")

row_prox <- c("\\multicolumn{17}{|c|}{Ethnic Asymmetric condition: Spatial Proximity}  \\\\\\hline\n",
   "Preference &  \\multicolumn{8}{|c|}{Ethnic Proximity} & \\multicolumn{8}{|c|}{Value Proximity}   \\\\\\hline\n",
  "& \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  & \\multicolumn{4}{|c|}{Local} & \\multicolumn{4}{|c|}{Minority}  \\\\\n",
"$\\beta$ sec = $\\beta$ doom   & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} & \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal} 
& \\multicolumn{2}{|c|}{Conservative} & \\multicolumn{2}{|c|}{Liberal}\\\\\n",
" & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD & Mean & SD\\\\\n")

tablerb_expname <- "latex/asym_all_rb_exp.tex"
tablerb_proxname <- "latex/asym_all_rb_prox.tex"

plotname <- "images/asym_all.jpg"

@@

fig_prox <- ggplot(data = data_prox, aes(x = dominant, y = Prox, linetype = `segregation` , fill = `ethnia`,  shape = `orientation`)) + geom_line(aes(color = `ethnia`))  +  geom_point(color = "black", size = 4) + 
 scale_x_discrete(limits=c(seq(0,20 ,by = 1))) + scale_y_continuous(limits=c(min(data_prox$Prox),max(data_prox$Prox)), breaks=seq(0,max(data_prox$Prox),by=0.50)) +
  geom_vline(xintercept = 20, color = "red") +
  scale_linetype_manual(values=c("solid","dashed"), labels = c("ethnic","value"), guide = guide_legend(title = "Segregation", order = 1)) +
  scale_fill_manual(values = c("blue","darkorange")) + 
  scale_color_manual(values = c("blue","darkorange"), guide = guide_legend(title="Ethnicity", order = 2)) + 
  scale_shape_manual(values = c(22,21), guide = guide_legend(title="Value" ,override.aes = list(size = 3), order = 3)) +
  guides(fill = FALSE) +
  xlab(xlab_t) + ylab(expression(Exposure[correct])) + 
  theme_bw() +  theme( axis.title.x = (element_text(size = 15)), axis.title.y = (element_text(size = 15)), axis.text.x =  (element_text(size = 15)),axis.text.y =  (element_text(size = 15)), legend.title = element_text(size = 13) ,legend.text = element_text(size = 13), plot.title=element_text(hjust = 0.5)) + theme(plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

```{r sa_etcnlc,  fig.cap="Fig. 17. Sensitivity ethnic conservative majority, asymmetric conditions", echo=FALSE}

# image output location

 scale_x_continuous(limits = c(min(xvalues),max(xvalues)), breaks = seq(0,max(xvalues), by = 0.5)) + 
  scale_y_continuous(breaks= seq(0,1,by=0.1)) + 
  geom_vline(xintercept = 1, color = "red") +
   xlab(expression(Exposure[correct])) + ylab("Exposure") +
  theme_bw() + theme( 
    axis.title.x = (element_text(size = 13)), axis.title.y = (element_text(size = 15)),
    axis.text.x =  (element_text(size = 12)), axis.text.y =  (element_text(size = 15)), 
    legend.title = element_text(size = 13),legend.position = "bottom", legend.text = element_text(size = 13),
    plot.title=element_text(hjust = 0.5), plot.caption = element_text(hjust= 0.5, size = 11), plot.margin=unit(c(0.1,0.1,0.1,0.1),"cm"))

@@

# Table Robustness Analysis

```{r sa_etcnlc_table,  fig.cap="Tab. 11: Sensitivity ethnic conservative majority, asymmetric conditions", echo=FALSE}
